Self Regulation Ontology Retest Data Report

### 2018-01-19 code/SRO_Report.Rmd
updating report for draft

# merge to get same number of rows for each subject at both time points
hr_merge = merge(t1_dvs, t2_dvs, by = c("worker_id", "breaks"))

@@

hr_merge = hr_merge %>%
  gather(key, value, -worker_id, -breaks) %>%
  separate(key, c("dv", "time"), sep="\\.") %>%
  mutate(time = ifelse(time == "x", 1, 2))

hr_merge

@@

# calculate point estimates for reliability of each of the variables for each break
# get_icc for each break of tmp_t1_dvs and tmp_t2_dvs
trial_num_rel_df = data.frame()
for(i in t1_dvs$breaks){
  tmp_t1_dvs = t1_dvs %>% filter(i)
  tmp_t2_dvs = t2_dvs %>% filter(i)
  trial_num_rel_df$breaks[i] = i
  trial_num_rel_df$acc_icc[i] = get_icc("acc", tmp_t1_dvs, tmp_t2_dvs)
  trial_num_rel_df$avg_rt_icc[i] = get_icc("avg_rt", tmp_t1_dvs, tmp_t2_dvs)
  trial_num_rel_df$score_icc[i] = get_icc("score", tmp_t1_dvs, tmp_t2_dvs)
}
```

>>>>

# merge to get same number of rows for each subject at both time points
hr_merge = merge(t1_dvs, t2_dvs, by = c("sub_id", "breaks"))

@@

hr_merge = hr_merge %>%
  gather(key, value, -sub_id, -breaks) %>%
  separate(key, c("dv", "time"), sep="\\.") %>%
  mutate(time = ifelse(time == "x", 1, 2))

@@

# calculate point estimates for reliability of each of the variables for each break
# get_icc for each break of tmp_t1_dvs and tmp_t2_dvs
trial_num_rel_df = data.frame(breaks=rep(NA, length(unique(t1_dvs$breaks))), acc_icc=rep(NA, length(unique(t1_dvs$breaks))), avg_rt_icc=rep(NA, length(unique(t1_dvs$breaks))), score_icc=rep(NA, length(unique(t1_dvs$breaks))))
for(i in 1:length(unique(t1_dvs$breaks))){
  cur_break = unique(t1_dvs$breaks)[i]
  tmp_t1_dvs = t1_dvs %>% filter(breaks == cur_break)
  tmp_t2_dvs = t2_dvs %>% filter(breaks == cur_break)
  trial_num_rel_df$breaks[i] = cur_break
  trial_num_rel_df$acc_icc[i] = get_icc("acc", tmp_t1_dvs, tmp_t2_dvs)
  trial_num_rel_df$avg_rt_icc[i] = get_icc("avg_rt", tmp_t1_dvs, tmp_t2_dvs)
  trial_num_rel_df$score_icc[i] = get_icc("score", tmp_t1_dvs, tmp_t2_dvs)
}
rm(i, cur_break, tmp_t1_dvs, tmp_t2_dvs)

trial_num_rel_df$breaks = as.numeric(trial_num_rel_df$breaks)

trial_num_rel_df %>%
  gather(key, value, -breaks) %>%
  ggplot(aes(breaks*10, value, color=factor(key, levels = c("acc_icc", "avg_rt_icc", "score_icc"), labels = c("Accuracy", "Average RT", "Score"))))+
  geom_point()+
  geom_line()+
  theme_bw()+
  xlab("Number of trials")+
  ylab("ICC")+
  theme(legend.title = element_blank())
```
